Occurrence and transmission potential of asymptomatic and pre-symptomatic SARS-CoV-2 infections: a living systematic review and meta-analysis

### 2021-10-28 Manuscript_draft.Rmd
manuscript commented

```{r table2, ft.split=TRUE, tab.cap='Table 1. Characteristics of studies included for Q2.1', echo = FALSE}
#create table
Q2_1_table <- Q2_1_table %>%
  arrange(setting)

table2 <- as_grouped_data(Q2_1_table, groups = "setting")
table2 <- flextable(table2)
table2 <- table2 %>%
  set_header_labels(setting = "Setting",
                    location = "Country, region", 
                    study = "Study") %>%
  set_table_properties(layout = "autofit") %>%
  theme_vanilla()
table2 <- width(table2, width = 10)
table2

Q2_1_table <- Q2_1_table %>%
  arrange(setting)
table2 <- as_grouped_data(Q2_1_table, groups = "setting")
table2 %>%
  as_flextable() %>%
  set_header_labels(setting = "Setting",
                    location = "Country, region", 
                    study = "Study") %>%
  set_table_properties(layout = "autofit") %>% fit_to_width(20) %>% 
  theme_vanilla()

>>>>

```{r table2, ft.split=TRUE, tab.cap='Table 1. Characteristics of studies included for Q2.1', echo = FALSE}
#create table
# Q2_1_table <- Q2_1_table %>%
#   arrange(setting)
# 
# table2 <- as_grouped_data(Q2_1_table, groups = "setting")
# table2 <- flextable(table2)
# table2 <- table2 %>%
#   set_header_labels(setting = "Setting",
#                     location = "Country, region", 
#                     study = "Study") %>%
#   set_table_properties(layout = "autofit") %>%
#   theme_vanilla()
# table2 <- width(table2, width = 10)
# table2
# 
# Q2_1_table <- Q2_1_table %>%
#   arrange(setting)
# table2 <- as_grouped_data(Q2_1_table, groups = "setting")
# table2 %>%
#   as_flextable() %>%
#   set_header_labels(setting = "Setting",
#                     location = "Country, region", 
#                     study = "Study") %>%
#   set_table_properties(layout = "autofit") %>% fit_to_width(20) %>% 
#   theme_vanilla()
